A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-12-31 paper/paper.tex
paper: arxiv-specific tweak to prose

Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ in indexed form, as the type of a coinductively-defined infinite sequence of type families representing the limit of $n$-truncated $\nu$-sets: $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n+1}, X_{n+2}, \ldots$ dependent on a $n$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$. This is made possible because the $0$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, defined to be in the unit type, and there is thus only one $0$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.

@@

Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that in this case the construction builds an effective sequence of types not mentioning coherences anymore. \\

>>>>

Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ in indexed form, as the type of a coinductively-defined infinite sequence of type families representing the limit of $n$-truncated $\nu$-sets: $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n+1}, X_{n+2}, \ldots$ dependent on a $n$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$. This is made possible because the $0$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, and there is thus only one $0$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.

@@

Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that the construction builds an effective sequence of types not mentioning coherences anymore. \\
